#extract data from espn
#create dataframe of outfield players and goal keepers
#merge two dataframe
#calculate the average goals of starting lineup players
```{r}
library(rvest)
library(xml2)
library(stringr)
library(tidyverse)
library(dplyr)
```
#extract data from website
```{r}
spider <- function(team_url){
    result = list()
    goalkeepers_result = list()
    outfield_players_result = list()

    print(team_url)
    html <- read_html(team_url)

    team_name <- html_nodes(html, '.n2') %>% html_text()

    tables <- html_nodes(html, xpath="//tbody[@class=\"Table2__tbody\"]")

    goalkeepers <- html_nodes(tables[1], xpath="tr[@class=\"Table2__tr Table2__tr--sm Table2__even\"]")
    
    for(index in 1:length(goalkeepers)){

        goalkeeper <- html_nodes(goalkeepers[index], xpath="td[@class=\"Table2__td\"]") %>% html_text()
        
        temp <- c(team_name, goalkeeper)
        
        goalkeepers_result[[index]] <- temp
        
    }

    outfield_players <- html_nodes(tables[2], xpath="tr[@class=\"Table2__tr Table2__tr--sm Table2__even\"]")
    for(index in 1:length(outfield_players)){

        outfield_player <- html_nodes(outfield_players[index], xpath="td[@class=\"Table2__td\"]") %>% html_text()
        
        temp <- c(team_name, outfield_player)
        
        outfield_players_result[[index]] <- temp
    }

    result[[1]] <- goalkeepers_result
    result[[2]] <- outfield_players_result
    
    return(result)
}
```
#extract data for each team
```{r}
all_goalkeepers_data = list()
all_outfield_players_data = list()

base_team_url <- "http://www.espn.com/soccer/team/squad/_/id/"
team_ids = c("349","359","331","379","347","363","383","368","370","335","375","364","382","360","361","376","367","395","371","380")

all_team_url <- paste(base_team_url, team_ids, sep = "")

for(team_url in all_team_url){
    tryCatch(
        {
            
            data <- spider(team_url)
            
            for (index in 1:length(data[[1]])){
                all_goalkeepers_data[[1+length(all_goalkeepers_data)]] <- data[[1]][[index]]
            }

            for (index in 1:length(data[[2]])){
                all_outfield_players_data[[1+length(all_outfield_players_data)]] <- data[[2]][[index]]
            }
        },
        
        error=function(e){
            print("********")
            cat(conditionMessage(e))
        }
    )
}
```
#tranfer to dataframe
```{r}
goalkeepers_df <- data.frame(matrix(unlist(all_goalkeepers_data), nrow=length(all_goalkeepers_data), byrow=T))
colnames(goalkeepers_df) <- c( 
    "team", "player",
    "POS", "AGE", "HT", "WT",
    "NAT", "APP", "SUBIN",	"S",
    "GC", "A", "FC", "FA",
    "YC", "RC"
)
goalkeepers_df
```
#transfer to dataframe
```{r}
outfield_players_df <- data.frame(matrix(unlist(all_outfield_players_data), nrow=length(all_outfield_players_data), byrow=T))
colnames(outfield_players_df) <- c( 
    "team", "player",
    "POS", "AGE", "HT", "WT",
    "NAT", "APP", "SUBIN", "G",
    "A", "SH", "ST", "FC",
    "FA",  "YC", "RC"
)
outfield_players_df
```
#save as csv file
```{r}
soccer_df <- bind_rows(goalkeepers_df, outfield_players_df)
write.csv(soccer_df, "soccer.csv")
```


# Load the data
```{r}
soccer <- read.csv("soccer.csv")
```
# Transfer the factor to numeric or character
```{r}
soccer[is.na(soccer)] <- 0
soccer$APP[which(soccer$APP == "-")] <- 0
soccer$APP <- as.numeric(as.character(soccer$APP))
soccer$G[which(soccer$G == "-")] <- 0
soccer$G[which(soccer$G == "#N/A")] <- 0
soccer$G <- as.numeric(as.character(soccer$G))
soccer$player <- as.character(soccer$player)
```

```{r}
avg_g <- function(teamname){
  sum = 0
  for(i in 1:11){
    G <- soccer$G[which(soccer$player == teamname[i])]
    APP <- soccer$APP[which(soccer$player == teamname[i])]
    temp <- G / APP
    sum = sum + temp
  }
  final <- sum / 11
  return(final)
}
```
# Manually input each team's starting lineup players
```{r}
teamname_1 = c("Kepa Arrizabalaga1","David Luiz30","Andreas Christensen27","Marcos Alonso3","César Azpilicueta28","Jorginho5","Mateo Kovacic17","N'Golo Kanté7","Gonzalo Higuaín9","Eden Hazard10","Pedro11")
final_1 <- avg_g(teamname_1)
final_1
teamname_2 = c("Ben Foster26","Craig Cathcart15","Adrian Mariappa6","José Holebas25","Kiko21","Abdoulaye Doucouré16","Nathaniel Chalobah14","Troy Deeney9","Gerard Deulofeu7","Roberto Pereyra37","Will Hughes19")
final_2 <- avg_g(teamname_2)
final_2
```


























































































